\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2021-02-16 iros-2021.tex
fixed font size in two figures
minor style changes

\begin{abstract}
  The paper presents a planning algorithm for autonomous UAVs with energy constraints and solves the problem of dynamic planning of the path and computations simultaneously. The planning strategy is based on a differential periodic energy model which is empirically motivated and formally proved. The model is enriched with the time and energy contribution of the path and computations. The algorithm replans both in the function of the battery state accounting for uncertainty and rescuing the UAV from a possible failure in case of unexpected changes of the battery state due to e.g., adverse atmospheric conditions.
\end{abstract}

@@

To achieve the energy-aware dynamic planning, we further introduce and formally prove a differential periodic energy model that accounts for the uncertainty. We use Fourier analysis to derive the model, and state estimation to address the uncertainty. Periodicity is often present due to repetitive patterns in the plan~\cite{seewald2020mechanical}. Indeed, UAV scenarios often iterate over a set of tasks and paths (e.g., monitoring or search and rescue). Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically. In Figure~\ref{fig:il-abs}, some collected energy data from a UAV flying a survey scenario along its power spectrum motivates our choice.

@@

  \begin{figure}[t]
    \centering
    \input{\figpath/traj1.tikz}
    \caption{Plan definition notation shown on an initial slice of the plan in Figure~\ref{fig:il-abs}.}
    \label{fig:traj1}
  \end{figure}

@@

\begin{figure}[h]
  \centering
  \input{\figpath/traj2.tikz}
  \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the path in Figure~\ref{fig:il-abs}).}
  \label{fig:tee1}
\end{figure}

@@

We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}. Left figures illustrate an initial slice of the estimation of the data and period $T$ (Proposition~\ref{prop:rank}). We used order $r$ equal to 3. We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate. On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a consistent state estimate. We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others. It hence approximates the non-periodicity with a linear model.

@@

We have tested the validity of Theorem~\ref{thm:state-vs-energy} showing the dynamic adaptation in the subfigure I.d of Figure~\ref{fig:ener}. We simulated two unexpected battery drops at approximately 1 minute and a half and 4 minutes and a half. The algorithm tries to maximize the parameter $c_2$ when the battery is discharging (plot on right) and reduces the path with parameter $c_1$ as the original plan cannot be completed with the current configuration of parameters. We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively.

@@

We are currently extending the results of this paper with an existing flying controller. We are further investigating the validity of the energy model on some other energy-critical mobile robots. For instance, we briefly investigated some possible implications on planetary exploration rovers in~\cite{seewald2020beyond}.

>>>>

\begin{abstract}
  The paper presents a planning algorithm for autonomous UAVs with energy constraints and solves the problem of dynamic planning of the path and computations simultaneously. The planning strategy is based on a periodic energy model that is empirically motivated and formally proved. The model is enhanced with the time and energy contribution of the path and computations. The algorithm replans both in the function of the battery state accounting for uncertainty and rescuing the UAV from a possible failure in case of unexpected changes of the power source due to, e.g., adverse atmospheric conditions.
\end{abstract}

@@

To achieve the energy-aware dynamic planning, we further introduce and formally prove a periodic energy model that accounts for the uncertainty. We use Fourier analysis to derive the model, and state estimation to address the uncertainty. Periodicity is often present due to repetitive patterns in the plan~\cite{seewald2020mechanical}. Indeed, UAV scenarios often iterate over a set of tasks and paths (e.g., monitoring or search and rescue). Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically. In Figure~\ref{fig:il-abs}, some collected energy data from a UAV flying a survey scenario along its power spectrum motivates our choice.

@@

  \begin{figure}[t]
    \centering
    \footnotesize
    \input{\figpath/traj1.tikz}
    \caption{Plan definition notation shown on an initial slice of the plan in Figure~\ref{fig:il-abs}.}
    \label{fig:traj1}
  \end{figure}

@@

\begin{figure}[h]
  \centering
  \footnotesize
  \input{\figpath/traj2.tikz}
  \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the path in Figure~\ref{fig:il-abs}).}
  \label{fig:tee1}
\end{figure}

@@

We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}. Left figures illustrate an initial slice of the model and period estimation (Proposition~\ref{prop:rank}). We used order $r$ equal to 3. We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate. On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a consistent state estimate. We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others. It hence approximates the non-periodicity with a linear model.

@@

We have tested the validity of Theorem~\ref{thm:state-vs-energy} showing the dynamic adaptation in the subfigure I.d of Figure~\ref{fig:ener}. We simulated two unexpected battery drops at approximately 1 minute and a half and 4 minutes and a half. The algorithm tries to maximize the parameter $c_2$ when the battery is discharging (plot on right) and reduces the path with parameter $c_1$ as the original plan cannot be completed with the current configuration of parameters. We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively, and a horizon $N$ equal to period $T$.

@@

We are currently extending the results of this paper with an existing flight controller. We are further investigating the validity of the energy model on some other energy-critical mobile robots. For instance, we briefly investigated some possible implications on planetary exploration rovers in~\cite{seewald2020beyond}.
